Network Configuration Synthesis with Abstract Topologies \vspace{1cm}

### 2017-03-15 paper/abstraction/appendix.tex
more refactoring

\todo{re evaluate this}

\todo{make explicit the fact that we can't anycast}

\todo{tie back to existing lemmas}

@@

    \vspace{1em}
    Assume that $\Topo(M) = f(a)$ and $\Topo(N) = f(b)$. \todo{This can be done because $f$ is surjective}. Also assume that $m'$ has a neighbor $n'$. We know that $\Topo(m) = a$ and $\Topo(m') = b$. Clearly $(a,b)$ is a valid concrete topology edge since it is a transition in the product graph between $m$ and $m'$. We now apply Lemma 7 with the following facts:

@@

\begin{defn}
  Assign $\Pref(m) = \Pref^A(f_{pg}(m))$ as increasing integers according to the total ordering for $\leq$.
  Clearly $\Pref(m) \leq \Pref(m') \iff m \leq m'$ and $\Pref(f_{pg}(m)) \leq \Pref(f_{pg}(m')) \iff f_{pg}(m) \leq f_{pg}(m')$
\end{defn}

@@

\todo{re evaluate this. I believe we need the proof of an inverse here}
\begin{lem}

@@

      \[ \begin{array}{l}
     ~~~~~ [~ l \rightarrow rc ~\vert~ \\
     ~~~~~~~~~~~~ l \in internal(G.V), ~rc = append_i \\
     ~~~~~~~~~~~~~~~ [~ pfx_i \rightarrow [~ ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ m \leftarrow (l,q_m) \in PG_i, \\
     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG_i,m), \\
     ~~~~~~~~~~~~~~~~~~~~~ (in,q_n) \leftarrow \{ (bs,q_n) ~\vert~ bs=\{b ~\vert~ (b,q_n) \in pin \}, bs \neq \emptyset \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_i,m) \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ ma = \Pref(m) : (in,q_n) \rightarrow (out,q_m) ~] ~] ~]\\
  \end{array} \]%

@@

  Apply the definition of $\Con$:

@@

@@

@@

  \[ \begin{array}{l}
     ~~~~~ [~ \ell \rightarrow rc ~\vert~ \\
     ~~~~~~~~~~~~ \ell \in f^{-1}(l), \\
     ~~~~~~~~~~~~ l \in internal(G^A.V), ~rc = append_i \\
     ~~~~~~~~~~~~~~~ [~ pfx_i \rightarrow [~ ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ (pfx_i, l') \in \Gamma(x), \\
     ~~~~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A, \\
     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A,M), \\
     ~~~~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ BS=\{B ~\vert~ (B,q_N) \in pin \}, BS \neq \emptyset \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A,M) \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ ma = \textbf{if } in = \{ G.start \} \textbf{ then } \bullet \\
     ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ \textbf{else } \Pref^A(M) : (\Con(in, \ell, \Gamma, f, G),q_N) \rightarrow (\Con(out, \ell, \Gamma, f, G), q_M) ~] ~] ~]\\
  \end{array} \]%

  \todo{magic happens here}

    \[ \begin{array}{l}
     ~~~~~ [~ \ell \rightarrow rc ~\vert~ \\
     ~~~~~~~~~~~~ \ell \in f^{-1}(l), \\
     ~~~~~~~~~~~~ l \in internal(G^A.V), ~rc = append_i \\
     ~~~~~~~~~~~~~~~ [~ pfx_i \rightarrow [~ ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ (pfx_i, l') \in \Gamma(x), \\
     ~~~~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A, \\
     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A,M), \\
     ~~~~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ BS=\{B ~\vert~ (B,q_N) \in pin \}, BS \neq \emptyset \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A,M) \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ ma = \textbf{if } in = \{ G.start \} \textbf{ then } \bullet \\
     ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ \textbf{else } \Pref^A(M) : (\Con(in, \ell, \Gamma, f, G),q_N) \rightarrow (\Con(out, \ell, \Gamma, f, G), q_M) ~] ~] ~]\\
  \end{array} \]%

  After filtering the cases where $in = \{ start \}$ and $l' \neq \ell$, we have the same situation as the previous case. 
  This works because each $PG_{ij}$ was constructed from $con(r_{ijk}) \cap end(l_{ij})$. This means that the only state in $PG_{ij}$ connected to the start node ($\mathit{start}$) is a node for $l_{ij}$. This was ensured by the fact that the transition function for each regular expression $\sigma_{ijk}(q_0,l) = q$ is defined only for locations $l \in L$ where $L = \{ l_{ij} \}$ from the construction of the automata.

    \[ \begin{array}{l}
     ~~~~~ [~ \ell \rightarrow rc ~\vert~ \\
     ~~~~~~~~~~~~ l \in internal(G.V), ~rc = append_i \\
     ~~~~~~~~~~~~~~~ [~ pfx_i \rightarrow [~ ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ (pfx_i, l') \in \Gamma(x), \\
     ~~~~~~~~~~~~~~~~~~~~~ m \leftarrow (l,q_m) \in PG_i, \\
     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG_i,m), \\
     ~~~~~~~~~~~~~~~~~~~~~ (in,q_n) \leftarrow \{ (bs,q_n) ~\vert~ bs=\{b ~\vert~ (b,q_n) \in pin \}, bs \neq \emptyset \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG_i,m) \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ ma = \Pref(m) : (in,q_n) \rightarrow (out,q_m)  ~] ~] ~]\\
  \end{array} \]%

>>>>

@@

    \vspace{1em}
    Assume that $\Topo(M) = f(a)$ and $\Topo(N) = f(b)$. Also assume that $m'$ has a neighbor $n'$. We know that $\Topo(m) = a$ and $\Topo(m') = b$. Clearly $(a,b)$ is a valid concrete topology edge since it is a transition in the product graph between $m$ and $m'$. We now apply Lemma 7 with the following facts:

@@

\begin{defn}
  Assign $\Pref(m) = \Pref^A(f_{pg}(m))$ as increasing integers according to the total ordering for $\leq$.
  Clearly from Lemma 9, $\Pref(m) \leq \Pref(m') \iff m \leq m'$ and $\Pref(f_{pg}(m)) \leq \Pref(f_{pg}(m')) \iff f_{pg}(m) \leq f_{pg}(m')$
\end{defn}

@@

\begin{lem}

@@

      \[ \begin{array}{l}
     ~~~~~ [~ l \rightarrow rc ~\vert~ \\
     ~~~~~~~~~~~~ l \in internal(G.V), ~rc = append_i \\
     ~~~~~~~~~~~~~~~ [~ pfx_i \rightarrow [~ ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ (pfx_i, \_) \in \Gamma(x), \\
     ~~~~~~~~~~~~~~~~~~~~~ m \leftarrow (l,q_m) \in PG_i, \\
     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG_i,m), \\
     ~~~~~~~~~~~~~~~~~~~~~ (in,q_n) \leftarrow \{ (bs,q_n) ~\vert~ bs=\{b ~\vert~ (b,q_n) \in pin \}, bs \neq \emptyset \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_i,m) \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ ma = \Pref_i(m) : (in,q_n) \rightarrow (out,q_m) ~] ~] ~]\\
  \end{array} \]%

@@

  \noindent
  We apply the definition of $\Con$ to push it inside the list:

@@

  \noindent
  We now apply the definition of $\Con$ to push it further inside:

@@

  \noindent
  Once again, we apply the definition of $\Con$

@@

  \noindent
  Once again, we apply the definition of $\Con$

  \[ \begin{array}{l}
     ~~~~~ [~ \ell \rightarrow rc ~\vert~ \\
     ~~~~~~~~~~~~ \ell \in f^{-1}(l), \\
     ~~~~~~~~~~~~ l \in internal(G^A.V), ~rc = append_i \\
     ~~~~~~~~~~~~~~~ [~ pfx_i \rightarrow [~ ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ (pfx_i, l') \in \Gamma(x), \\
     ~~~~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A, \\
     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A,M), \\
     ~~~~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ BS=\{B ~\vert~ (B,q_N) \in pin \}, BS \neq \emptyset \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A,M) \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ ma = \textbf{if } in = \{ G.start \} \text{ and } l'=\ell \textbf{ then } \bullet \\
     ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ \textbf{else } \Pref^A(M) : (\Con(in, \ell, \Gamma, f, G),q_N) \rightarrow (\Con(out, \ell, \Gamma, f, G), q_M) ~] ~] ~]\\
  \end{array} \]%

  After filtering the cases where $in = \{ start \}$ and $l' \neq \ell$, we have the same situation as the previous case. 
  This works because each $PG_{i}$ was constructed from $con(r_{i}, \ell, \Gamma, f, G) \cap end(l_{i})$. This means that the only state in $PG_{i}$ connected to the start node ($\mathit{start}$) is a node for $l_{i}$. This was ensured by the fact that the transition function for each regular expression $\sigma_{i}(q_0,l) = q$ is defined only for locations $l \in L$ where $L = \{ l_{i} \}$ from the construction of the automata.

    \[ \begin{array}{l}
     ~~~~~ [~ \ell \rightarrow rc ~\vert~ \\
     ~~~~~~~~~~~~ l \in internal(G.V), ~rc = append_i \\
     ~~~~~~~~~~~~~~~ [~ pfx_i \rightarrow [~ ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ (pfx_i, l') \in \Gamma(x), \\
     ~~~~~~~~~~~~~~~~~~~~~ m \leftarrow (l,q_m) \in PG_i, \\
     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG_i,m), \\
     ~~~~~~~~~~~~~~~~~~~~~ (in,q_n) \leftarrow \{ (bs,q_n) ~\vert~ bs=\{b ~\vert~ (b,q_n) \in pin \}, bs \neq \emptyset \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG_i,m) \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ ma = \Pref_i(m) : (in,q_n) \rightarrow (out,q_m)  ~] ~] ~]\\
  \end{array} \]%

\vspace{2em}
\begin{thm}
  For all \sysname policies $pol$, contexts $\Gamma$, topologies $G$ and $G^A$ related by homomorphism $f : G \rightarrow G^A$:
  $$\Con(\Compile(pol,G^A),\Gamma,f,G) = \Compile(\Con(pol,\Gamma,f),G)$$

  \begin{proof} 
    $ $

    \vspace{.5em}
    \noindent
    Given a policy $pol = p_1, \ldots, p_n$ we apply Theorem 11 after rewriting the policy. For the left side:
    \[
    \begin{array}{llll}
      & & \Con(\Compile(pol,G^A),\Gamma,f,G) \\
      &=& \Con(\Compile(p_1, \ldots, p_n, G^A),\Gamma,f,G) & \text{Substitution} \\
      &=& \Con(\CompileMbgp([\CompilePg(p_1), \ldots, \CompilePg(p_n)]),\Gamma,f,G)
            & \text{Definition of Compile} \\
      &=& \Con(\CompileMbgp([(t_1,PG^A_1,\Pref^A_1), \ldots, (t_n,PG^A_n,\Pref^A_n)]),\Gamma,f,G)
            & \text{Assumption}\\
    \end{array}
    \]

    \vspace{.5em}
    \noindent
    For the right side of the equation:
    \[
    \begin{array}{llll}
      & & \Compile(\Con(pol,\Gamma,f),G) \\
      &=& \Compile(\Con(p1,\dots,p_n, \Gamma,f), G) 
            & \text{Substitution} \\
      &=& \Compile(\Con(p1, \Gamma, f),\dots, \Con(p_n, \Gamma,f), G) 
            & \text{Definition of con} \\
      &=& \CompileMbgp([\CompilePg(\Con(p1, \Gamma, f),G), \ldots, \CompilePg(\Con(p_n, \Gamma, f),G)]) 
            & \text{Definition of compile} \\

      &=& \CompileMbgp([(t'_1, PG_1, \Pref_1), \ldots, (t'_n, PG_n, \Pref_n)])
            & \text{Assumption} \\

    \noindent
    First, we observe that, for each $p_i$, Theorem 11 and $\CompilePg$ give us that, for each $i$:
    \[ \begin{array}{l}
     ~~~~~ [~ \ell \rightarrow rc ~\vert~ \\
     ~~~~~~~~~~~~ l \in internal(G^A.V), \\ 
     ~~~~~~~~~~~~ rc = [\CompilePred((t_i, PG^A_i, \Pref^A_i))] ~~] \\
    \end{array} \]%

    \noindent
    Is equivalent to:

    \[ \begin{array}{l}
     ~~~~~ [~ \ell \rightarrow rc ~\vert~ \\
     ~~~~~~~~~~~~ l \in internal(G.V), \\ 
     ~~~~~~~~~~~~ rc = [\CompilePred((t'_i, PG_i, \Pref_i))] ~~] \\
    \end{array} \]%

    \noindent
    By applying the definition of $\CompileMbgp$, we need to show:

    \[ \begin{array}{l}
     ~~~~~ [~ \ell \rightarrow rc ~\vert~ \\
     ~~~~~~~~~~~~ l \in internal(G^A.V), \\ 
     ~~~~~~~~~~~~ rc = append_{i \in \{1..n\}}(\CompilePred((t_i, PG^A_i, \Pref^A_i))) ~] \\
    \end{array} \]%

    \[ \begin{array}{l}
     ~~~~~ [~ \ell \rightarrow rc ~\vert~ \\
     ~~~~~~~~~~~~ l \in internal(G.V), \\ 
     ~~~~~~~~~~~~ rc = append_{i \in \{1..n\}}(\CompilePred((t'_i, PG_i, \Pref_i))) ~] \\
    \end{array} \]%

    \noindent
    Clearly this follows by the definition of list $\mathrm{append}$
